Rush hour subways surprisingly excel at punctuality: a closer look at TTC Delays

### 2024-09-27 paper/paper.qmd
final, minor, modifications to the paper

Accounting for the previously mentioned carry-over delay for the specific subway arriving at each of the 4 stations, we conclude that for the average trip during peak hour, leaving 10-15 minutes early is a fairly safe margin to ensure punctual arrival even in the case of delays, doubling this value to account for extra stations (20-30 minutes extra for an 8-station trip, for example).

>>>>

Accounting for the previously mentioned carry-over delay for the specific subway arriving at each of the 4 stations, we conclude that for the average trip during peak hour, leaving 10-15 minutes early is a fairly safe margin to ensure punctual arrival even in the case of delays, scaling this value as fit to account for extra/fewer stations (leave a 20-30 minutes margin for an 8-station trip, for example).
